---
title: "Data visualization"
author: "sch"
date: "11/14/2021"
output: html_document
---

```{r setup, include=FALSE}
##input data, packages installation
library(ggplot2)
library(dplyr)
library(magrittr)
library(readxl)
library('scales')
dataset_visualization_ <- read_excel("test2.xlsx") ##insert the excel file
View(dataset_visualization_)
monthweeks <- function(x) {
    UseMethod("monthweeks")
}
monthweeks.Date <- function(x) {
    ceiling(as.numeric(format(x, "%d")) / 7)
}
monthweeks.POSIXlt <- function(x) {
    ceiling(as.numeric(format(x, "%d")) / 7)
}
monthweeks.character <- function(x) {
    ceiling(as.numeric(format(as.Date(x), "%d")) / 7)
}

dataset_visualization_ =dataset_visualization_%>%mutate(month=months(dataset_visualization_$start_time,abbreviate = TRUE))
dataset_visualization_ =dataset_visualization_%>%mutate(Date=as.Date(dataset_visualization_$start_time))
dataset_visualization_ =dataset_visualization_%>%mutate(WOM=monthweeks(dataset_visualization_$Date))


##Time Scale Selection 
date1 <- "2021-01-15" #Start
date2 <- "2021-07-15" #End
dataset_visualization_ =dataset_visualization_%>%filter(Date>date1)%>%filter(Date<date2)
```




##Monthly Trespassing Event Totals
```{r pressure, echo=FALSE}
##Monthly Trespassing Event Total
dataset1 = dataset_visualization_%>% filter(Validation == TRUE)
#fig(20,8)
baselayer =  ggplot( aes(factor(month,levels = c('Jan','Feb','Mar','Apr','May','Jun','Jul','Aug','Sep','Oct','Nov','Dec')),fill = type),data = dataset1)+
  geom_bar(stat="count", position='dodge',width = 0.5)+  # Dodge for group
 labs(x="Month/Type",
         y="count", 
       title="Monthly Trespassing Event Totals: ") +
theme_bw()#+
  geom_text(aes(label=type)) #+
theme(plot.title = element_text(size=18),axis.text.x= element_text(size=15,angle=90),
                            axis.text.y= element_text(size=15), axis.title=element_text(size=18))

plot(baselayer)
```

##Monthly Trespassing Event Totals(seperated by type)
```{r}
#fig(12,8)
dataset1 = dataset_visualization_%>% filter(Validation == TRUE)
ggplot(dataset_visualization_, aes(factor(month,levels = c('Jan','Feb','Mar','Apr','May','Jun','Jul','Aug','Sep','Oct','Nov','Dec'))))+
geom_bar(stat="count", width = 0.5,aes(fill=type))+
 labs(x="",
         y="Count", 
       title="Distribution of Trespass in General")+ 
facet_wrap(~type)+
theme_bw()+
theme(plot.title = element_text(size=11),axis.text.x= element_text(size=8,angle=90),
                            axis.text.y= element_text(size=8), axis.title=element_text(size=9))
```

##Trespassing Event Totals Day of Hour(In one month)
```{r}
#fig(12,8)
dataset1 = dataset_visualization_%>% filter(Validation == TRUE)%>% filter(month == 'Jul') ## choose month

ggplot(dataset1, aes(as.integer(HOD)))+
geom_bar(stat="count", width = 0.5,aes(fill=type))+xlim(0,23)+
 labs(x="Hour of the Day",
         y="Count", 
       title="Monthly Trespassing Event Totals Day of Hour: Jan")+ 
facet_wrap(~type)+
theme_bw()+
theme(plot.title = element_text(size=11),axis.text.x= element_text(size=6,angle=90),
                            axis.text.y= element_text(size=8), axis.title=element_text(size=9))
```
##Heatap of the tresspass in one month
```{r}
#Change the following parameters to select the month
dataset1 = dataset_visualization_%>% filter(Validation == TRUE)%>% filter(month == 'Jun')
#
dataset1 = dataset1%>% group_by(WOM,DOW,HOD,type)%>% summarise(across(.cols ='_id',list(num = length)))
dataset2 = cbind(c(rep('car',840),rep('bus',840),rep('person',840),rep('truck',840),rep('bicycle',840)))
dataset2 = cbind(dataset2,c(rep('week1',168),rep('week2',168),rep('week3',168),rep('week4',168),rep('week5',168)))
dataset3 = cbind(c(rep('Mon',24),rep('Tue',24),rep('Wed',24),rep('Thu',24),rep('Fri',24),rep('Sat',24),rep('Sun',24)))
dataset2 = cbind(dataset2,rep(dataset3,5))
dataset3 = cbind(1:24)
dataset_final = cbind(dataset2,rep(dataset3,175),rep(0,4200))
n = nrow(dataset1)
for (i in 1:n) {
  r = 0
  t = dataset1[i,4]
  w = dataset1[i,1]
  d = dataset1[i,2]
  h = dataset1[i,3]
  x = dataset1[i,5]
  w = as.integer(w)
  d = as.integer(d)
  h = as.integer(h)
  x = as.integer(x)
  if(t =='bus'){
    r = r+840
  }
  if(t =='person'){
    r = r+840*2
  }
  if(t =='truck'){
    r = r+840*3
  }
  if(t =='bicycle'){
    r = r+840*4
  }
  r =r + (w-1)*168 + (d-1)*24 + h + 1
  dataset_final[r,5] = x
}
dataset_final= data.frame(type= dataset_final[,1],WOM = dataset_final[,2],DOW= dataset_final[,3],HOD= dataset_final[,4],num= dataset_final[,5])
dataset_final[,5] = type.convert(dataset_final[,5])
dataset_final[,4] = type.convert(dataset_final[,4])

baselayer = ggplot(dataset_final,aes(HOD, factor(DOW,levels = c('Mon','Tue','Wed','Thu','Fri','Sat','Sun')),fill = num)) +
 geom_tile() +
 facet_grid(type~WOM)+
 scale_fill_gradient(low = "white", high = "red", guide = "legend")+
 labs(x="Hour of Day",
       y="",
       title = "Total Trespass Heatmap of A Month", 
       fill="count")+
 theme_bw()+
 theme(plot.title = element_text(size=11)
      ,axis.text.x= element_text(size = 6),
       axis.text.y= element_text(size=6),
        axis.title=element_text(size=9))
baselayer
```

##Trespass Event by Week of the Month
```{r}

#fig(12,8)
dataset1 = dataset_visualization_%>% filter(month == 'Jul') ##choose the certain month
ggplot(dataset1, aes(factor(WOM)))+
geom_bar(stat="count", width = 0.5,aes(fill=type))+
 labs(x="",
         y="Count", 
       title="Trespass Event by Week of the Month")+ 
facet_wrap(~type)+
theme_bw()+
theme(plot.title = element_text(size=11),axis.text.x= element_text(size=6,angle=90),
                            axis.text.y= element_text(size=8), axis.title=element_text(size=9))
```

##Trespass Event by in a Week of the Month

```{r}
##choose the month and the num of the week in next line
dataset1 = dataset_visualization_%>% filter(month == 'Jun')%>% filter(WOM == 3) 

ggplot(dataset1, aes(factor(DOW)))+
geom_bar(stat="count", width = 0.5,aes(fill=type))+
 labs(x="",
         y="Count", 
       title="Ramsey, NJ Detection Grade Crossing Trespass Event by Day of Hour: Jan")+ 
facet_wrap(~type)+
theme_bw()+
theme(plot.title = element_text(size=11),axis.text.x= element_text(size=8,angle=90),
                            axis.text.y= element_text(size=8), axis.title=element_text(size=9))
```
##Trespass Event Day By Hour In A Certain Day
```{r}

##Select the Month And Week In following Line
dataset1 = dataset_visualization_%>% filter(Validation == TRUE)%>% filter(month == 'Jul')%>% filter(WOM == 3)%>% filter(DOW == '1')

#dataset1$HOD = as.numeric()
ggplot(dataset1, aes(as.integer(HOD)))+xlim(0,23)+
geom_bar(stat="count", width = 0.4,aes(fill=type))+
 labs(x="",
         y="Count", 
       title="Ramsey, NJ Detection Grade Crossing Trespass Event by Day by Hour: Jan")+ 
facet_wrap(~type)+
theme_bw()+
theme(plot.title = element_text(size=11),axis.text.x= element_text(size=8,angle=90),
                            axis.text.y= element_text(size=8), axis.title=element_text(size=9))
```
##Total Weather Distribution(Hist)
```{r}
dataset_weather = dataset_visualization_%>% filter(Validation == TRUE) %>% group_by(weather) %>% summarise(across(.cols = 'Validation',list(num=length)))
total = sum(dataset_weather[,2])
dataset_weather$percentage<-(round((dataset_weather[,2])/total,2))


ggplot(dataset_weather, aes(weather,Validation_num,fill=Validation_num))+
geom_bar(stat="identity", width = 0.5)+
geom_text(aes(label=Validation_num, vjust=0)) +
scale_fill_gradient(low = "green", high = "red")+
 labs(x="Weather",
         y="Percentage", 
       title="Distribution of Playstore Genres ")+ 
theme_bw()+
theme(plot.title = element_text(size=22),axis.text.x= element_text(size=15,angle=90),
                            axis.text.y= element_text(size=15), axis.title=element_text(size=18))

```

##Total Weather Distribution(Pie)
```{r}
dataset_weather = dataset_visualization_%>% filter(Validation == TRUE) %>% group_by(weather) %>% summarise(across(.cols = 'Validation',list(num=length)))
total = sum(dataset_weather[,2])
dataset_weather$percentage<-(round(dataset_weather[,2]/total,2))
dataset_weather[,2] = type.convert(dataset_weather[,2])
dataset_weather[,3] = type.convert(dataset_weather[,3])

ggplot(dataset_weather, aes(x = "", y=Validation_num, fill = weather)) + 
  geom_bar(width = 1, stat = "identity") +coord_polar(theta = "y", start=0)+
scale_fill_brewer(palette="Set2")+
  labs(fill="weather", 
       x=NULL, 
       y=NULL, 
       title="Pie Chart of Weather") +
  theme(axis.ticks = element_blank()) +
  theme(axis.text.x = element_blank())+ 
geom_text(aes(label = percent(Validation_num/total)),size=3.5, position = position_stack(vjust = 0.4))+
theme_void()+theme(plot.title = element_text(hjust=0.8,size=20))#+
scale_y_continuous(breaks = dataset_weather$Validation_num)
```

##Monthly Weather/Tresspass
```{r}
#fig(12,8)
dataset1 = dataset_visualization_%>% filter(Validation == TRUE)
ggplot(dataset1, aes(month))+
geom_bar(stat="count", width = 0.5,aes(type,fill=type))+
 labs(x="",
         y="Count", 
       title="Distribution of Trespass in General")+ 
facet_grid(weather~month)+
theme_bw()+
theme(plot.title = element_text(size=11),axis.text.x= element_text(size=8,angle=90),
                            axis.text.y= element_text(size=8), axis.title=element_text(size=9))

```

##Grade Total Crossing Trespass Detection(True And False)
```{r}
 ggplot( aes(month,fill = Validation),data = dataset_visualization_)+
  geom_bar(stat="count", position='dodge',width = 0.5)#+  # Dodge for group
 labs(x="Hour",
         y="count", 
       title="Ramsey, NJ Detection Grade Crossing Trespass Detection") +
theme_bw()#+
  geom_text(aes(label=type)) #+
theme(plot.title = element_text(size=18),axis.text.x= element_text(size=15,angle=90),
                            axis.text.y= element_text(size=15), axis.title=element_text(size=18))


```

##Grade Total Crossing Trespass Detection(False) by Type
```{r}
#fig(12,8)
dataset1 = dataset_visualization_%>% filter(Validation == FALSE)
ggplot(dataset1, aes(HOD))+
geom_bar(stat="count", width = 0.5,aes(fill=type))+
 labs(x="",
         y="Count", 
       title="Distribution of Netflix Shows in India,US,UK & Australia")+ 
facet_grid(Explanation~type)+
theme_bw()+
theme(plot.title = element_text(size=11),axis.text.x= element_text(size=8,angle=90),
                            axis.text.y= element_text(size=8), axis.title=element_text(size=9))
```
##Grade Crossing Trespass Detection(False) By Type In One Month
```{r}
#Change the following parameters to select the month
dataset1 = dataset_visualization_%>% filter(Validation == FALSE)%>% filter(month == 'Jul')
#
dataset1 = dataset1%>% group_by(WOM,DOW,HOD,type)%>% summarise(across(.cols ='_id',list(num = length)))
dataset2 = cbind(c(rep('car',840),rep('bus',840),rep('person',840),rep('truck',840),rep('bicycle',840)))
dataset2 = cbind(dataset2,c(rep('week1',168),rep('week2',168),rep('week3',168),rep('week4',168),rep('week5',168)))
dataset3 = cbind(c(rep('Mon',24),rep('Tue',24),rep('Wed',24),rep('Thu',24),rep('Fri',24),rep('Sat',24),rep('Sun',24)))
dataset2 = cbind(dataset2,rep(dataset3,5))
dataset3 = cbind(1:24)
dataset_final = cbind(dataset2,rep(dataset3,175),rep(0,4200))
n = nrow(dataset1)
for (i in 1:n) {
  r = 0
  t = dataset1[i,4]
  w = dataset1[i,1]
  d = dataset1[i,2]
  h = dataset1[i,3]
  x = dataset1[i,5]
  w = as.integer(w)
  d = as.integer(d)
  h = as.integer(h)
  x = as.integer(x)
  if(t =='bus'){
    r = r+840
  }
  if(t =='person'){
    r = r+840*2
  }
  if(t =='truck'){
    r = r+840*3
  }
  if(t =='bicycle'){
    r = r+840*4
  }
  r =r + (w-1)*168 + (d-1)*24 + h + 1
  dataset_final[r,5] = x
}
dataset_final= data.frame(type= dataset_final[,1],WOM = dataset_final[,2],DOW= dataset_final[,3],HOD= dataset_final[,4],num= dataset_final[,5])
dataset_final[,5] = type.convert(dataset_final[,5])
dataset_final[,4] = type.convert(dataset_final[,4])

baselayer = ggplot(dataset_final,aes(HOD, factor(DOW,levels = c('Mon','Tue','Wed','Thu','Fri','Sat','Sun')),fill = num)) +
 geom_tile() +
 facet_grid(type~WOM)+
 scale_fill_gradient(low = "white", high = "red", guide = "legend")+
 labs(x="Hour of Day",
       y="",
       title = "Total Trespass Heatmap of A Month", 
       fill="count")+
 theme_bw()+
 theme(plot.title = element_text(size=11)
      ,axis.text.x= element_text(size = 6),
       axis.text.y= element_text(size=6),
        axis.title=element_text(size=9))
baselayer
```

